Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2019-02-05 Manuscript/manuscript.tex
Written PC-PS interaction section

\todo{SAMULI: Lipid17 simulations are too compressed, which is probably due to the
  overbinding of Dang ions. Lipid17 with Åqvist ions (default in Amber) has larger
  area in NMRlipids IV. This is similar to ECC-POPC paper where changing from Åqvist to
  Dang or ECC-ions increased binding affinity in Lipid14. However, the headgroup order
  parameters are better in ECC-POPS compared to Lipid17 simulations with any ions.
  These should be discussed in this section.
}

@@

The head group and acyl chain order parameters within ECC-lipids
are in general in a good agreement with the experimental values 
as shown in Fig. \ref{simVSexpNOions_POPS}. 
The acyl chain order parameters in particular agree with the experimental data within error bars.
The order parameters of the head groups are at an accuracy comparable to 
other currently available classical models of lipids \citep{botan15, catte16, Pluhackova2016, nmrlipids_proj4}.

The head group order parameters $\alpha$ and $\beta$ are highly relevant for this work,
as they are being used in the electrometer concept \cite{altenbach84, catte16, melcr18}.
%For POPC in pure water, the order parameter $\beta$ agrees well with the experiment, while the order parameter $\alpha$ is somewhat lower. 
The head group order parameters of PS are a bit more complicated 
compared to PC as the order parameter $\alpha$ exhibits a notable forking 
(i.e., the hydrogen atoms in the group give rise to different order parameters, see Fig.~\ref{simVSexpNOions_POPS}).
One of the order parameters of ECC-POPS, $\alpha_1$, agrees well with the experiment, 
while the other, $\alpha_2$, adopts a higher value underestimating the experimentally reported forking. 
There is only one order parameter $\beta$ in POPS, 
which has a higher value closer to zero in the ECC-lipids model than in experiment. 
Such a feature suggests that the model likely overestimates the orientational freedom of the PS head group.

@@

Changes of the lipid bilayer head group order parameters extracted from simulations and 
experiments \cite{roux90} are shown in Figs.~\ref{fig:delta_ordPar_KCl_PCPS}, \ref{fig:delta_ordPar_NaCl_PCPS} 
and~\ref{fig:delta_ordPar_CaC_PCPS} as functions of KCl, NaCl or CaCl$_2$ concentrations,
and in Figs.~\ref{fig:delta_ordPar_NaCl_PC-PS_mix} as a function of PC and PS content.

\todo{EDIT: Taken from NMRlipids4 as an interesting information, to be edited.}
The headgroup order parameters
of negatively charged PS and PG lipids exhibit systemic, but less
characterized dependence on the bound charge~\cite{borle85,macdonald87,roux86,roux90}.
Therefore, the ion binding affinity to negatively charged bilayers
can be better characterized by measuring the PC headgroup order parameters from 
mixed bilayers~\cite{roux86,roux90,roux91},

\todo{EDIT: Taken from NMRlipids4 as an interesting information, to be edited.}
Previous experimental studies have concluded that
PS headgroups are more rigid than phophocholines (PC)
due to the hydrogen bonding network or
electrostatic interactions \cite{browning80,buldt81}.
%
Dilution of bilayers with PC lipids makes PS headgroups
less rigid and reduces propensity for the formation of
strong complexes with multivalent ions \cite{browning80,buldt81,roux90,roux91}.
The molecular level interpretation of these observations is,
however, not available.

\begin{figure*}[!tbp] 
  \centering 
  \includegraphics[height=\figheightsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_nacl.pdf} 
  \includegraphics[height=\figheightsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_nacl.pdf} 
  \includegraphics[height=\figheightsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_kcl.pdf} 
  \includegraphics[height=\figheightsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_kcl.pdf} 
  \caption{\label{fig:delta_ordPar_NaCl_PC-PS_mix} 
    The head group order parameters of a POPC:POPS (5:1) bilayer as a function of PS content
    with \ce{Na^+} and \ce{K^+} counterions from simulations with ECC-lipids and Lipid17 \cite{lipid17-future} 
    and experiments (only \ce{Na^+} counterions). \cite{roux90}. 
    The underestimated response of ECC-lipids with \ce{Na^+} counterions 
    is likely due to a still slightly overestimated binding affinity of \ce{Na^+} to the phospholipids,
    which is corroborated by the series with \ce{K^+} counterions (lower affinity than \ce{Na^+}),
    where the response is closer to the experiment (which uses only \ce{Na^+} counterions). 
  }
\end{figure*}

@@

>>>>

@@

The head group and acyl chain order parameters within ECC-lipids
are in general in a good agreement with the experimental values 
as shown in Fig. \ref{simVSexpNOions_POPS}. 
The acyl chain order parameters in particular agree with the experimental data within error bars.
The order parameters of the head groups are at an accuracy comparable to 
other currently available classical models of lipids \citep{botan15, catte16, Pluhackova2016, nmrlipids_proj4}. 
In particular, ECC-POPS is closer to the experimental order parameters 
than Lipid17 with either Dang \cite{smith94,chang1999,dang2006} 
or ff99 ions \citet{aqvist90}.

%The head group order parameters $\alpha$ and $\beta$ are highly relevant for this work,
%as they are being used in the electrometer concept \cite{altenbach84, catte16, melcr18}.
%For POPC in pure water, the order parameter $\beta$ agrees well with the experiment, while the order parameter $\alpha$ is somewhat lower. 
The head group order parameters of PS are a bit more complicated 
compared to PC as the order parameter $\alpha$ exhibits a notable forking 
(i.e., the hydrogen atoms in the group give rise to different order parameters, see Fig.~\ref{simVSexpNOions_POPS}).
One of the order parameters of ECC-POPS, $\alpha_1$, agrees well with the experiment, 
while the other, $\alpha_2$, adopts a higher value underestimating the experimentally reported forking. 
There is only one order parameter $\beta$ in POPS, 
which has a higher value closer to zero in the ECC-lipids model than in experiment. 
Such a feature suggests that the model likely overestimates the orientational freedom of the PS head group.

@@

According to the electrometer concept,
the head group order parameters $\alpha$ and $\beta$ of PC lipids
change proportionally to the amount of bound charge
in a fixed ratio. \cite{seelig87,scherer87,roux90} 
This was demonstrated for a bound positive charge in simulations with POPC and 
cationic surfactants or aquaeous cations employing the ECC-POPC model \cite{melcr18}.
In this work, we will use the electrometer concept also for a bound negative charge 
using PS lipids as negatively charged surfactants. \cite{roux90}

Unlinke in pure PC bilayers,
Interpreting the changes of the head group order parameters of 
mixed PC:PS lipid bilayers 
from both simulations and experiments
is complicated by the presence of counterions. \cite{nmrlipids_proj4}
In order to see the effects of different counterions, 
we performed simulations with \ce{Na+} and also with \ce{K+} counterions, 
which bind more weakly to phospholipids. \cite{nmrlipids_proj4, melcr18}
This can also be seen in the density plots of the counterions in Fig.~\ref{fig:POPS-counterions-dens},
which show a significantly reduced concentration of \ce{K+} ions 
at the membrane head group region compared to \ce{Na+}
for both PS and mixed PC:PS (5:1) bilayers.

The slopes of the response of the PC head group order parameters $\alpha$ and $\beta$ 
in the mixed PC:PS (5:1) bilayer with \ce{K+} counterions
(Fig.~\ref{fig:delta_ordPar_NaCl_PC-PS_mix})
agree qualitatively well with experiments for both employed models,
i.e., for both Lipid14/17 and ECC-lipids. 
The same property from the simualtions with \ce{Na+} counterions, 
which were used in the experimental measurement,
are not as good, however.
In particular,
ECC-lipids have a weaker response of their PC head group order parameters compared to the experiments, 
while the simulations with Lipid17 model reveal a completely opposite trend.
This effect likely arises from an overestimated binding of the sodium cations to the phospholipids \cite{nmrlipids_proj4},
which is likely still present in a small amount also in the simulations with ECC-lipids. 
The large difference between the affinities of the employed lipid models to the counterions 
is visible in the density plots in Fig~\ref{fig:POPS-counterions-dens}.

The order parameters of the PS head groups including their changes with the content of PC lipids
are challenging to capture correctly in classical MD simulation models. \cite{nmrlipids_proj4}
From such a perspective,
the changes of the PS head group order parameters from ECC-lipids 
with \ce{Na+}, and also \ce{K+}, counterions 
agree comparably well to the experimental measurements
(Fig.~\ref{fig:delta_ordPar_NaCl_PC-PS_mix}). 
Interestingly enough, 
although the Lipid17 model performed well with \ce{K+} counterions 
for the PC head group order parameter changes,
it does not agree in the equivalent changes in PS head groups
pointing at non-negligible effects of even relatively weakly binding cations 
on the structure of negatively charged lipids.

Despite the great improvements in the overall structure of ECC-POPS 
and its response to PC lipids and counterions,
there is still a large room for improving it
to agree with the experimental measurements.

\begin{figure*}[!tbp] 
  \centering 
  \includegraphics[height=\figheightsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_nacl.pdf} 
  \includegraphics[height=\figheightsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_nacl.pdf} 
  \includegraphics[height=\figheightsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_kcl.pdf} 
  \includegraphics[height=\figheightsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_kcl.pdf} 
  \caption{\label{fig:delta_ordPar_NaCl_PC-PS_mix} 
    The head group order parameters of a POPC:POPS (5:1) bilayer as a function of PS content
    with \ce{Na^+} (top) and \ce{K^+} (bottom) counterions from simulations with ECC-lipids and Lipid17 \cite{lipid17-future} 
    and experiments (only \ce{Na^+} counterions, but shown also in bottom plots). \cite{roux90}. 
    The underestimated response of ECC-lipids with \ce{Na^+} counterions 
    is likely due to a still slightly overestimated binding affinity of \ce{Na^+} to the phospholipids,
    which is corroborated by the series with \ce{K^+} counterions (lower affinity than \ce{Na^+}),
    where the response is closer to the experiment, which uses only \ce{Na^+} counterions. 
  }
\end{figure*}

@@

\todo{EDIT: Taken from NMRlipids4 as an interesting information, to be edited.}
The headgroup order parameters
of negatively charged PS and PG lipids exhibit systemic, but less
characterized dependence on the bound charge~\cite{borle85,macdonald87,roux86,roux90}.
Therefore, the ion binding affinity to negatively charged bilayers
can be better characterized by measuring the PC headgroup order parameters from 
mixed bilayers~\cite{roux86,roux90,roux91},
%
Previous experimental studies have concluded that
PS headgroups are more rigid than phophocholines (PC)
due to the hydrogen bonding network or
electrostatic interactions \cite{browning80,buldt81}.
%
Dilution of bilayers with PC lipids makes PS headgroups
less rigid and reduces propensity for the formation of
strong complexes with multivalent ions \cite{browning80,buldt81,roux90,roux91}.
The molecular level interpretation of these observations is,
however, not available.

Figs.~\ref{fig:delta_ordPar_KCl_PCPS}, \ref{fig:delta_ordPar_NaCl_PCPS} 
and~\ref{fig:delta_ordPar_CaCl_PCPS} as functions of KCl, NaCl or CaCl$_2$ concentrations,
and in Figs.~\ref{fig:delta_ordPar_NaCl_PC-PS_mix} as a function of PC and PS content.
